Scheeper's Meager-NWD Game and the Menger Game

### 2014-05-07 phd/dissertation/chapter2.tex
More work on expository chapter

Topological games are usually infinite games. One of the earliest examples
of a topological game is the Banach Mazur game, proposed by Stanislaw Mazur
as Problem 43 in Stefan Banach's Scottish Book (1935). We give a more
general definition here.

@@

@@

@@

>>>>

Topological games are usually infinite games. One of the earliest examples
of a topological game is the Banach-Mazur game, proposed by Stanislaw Mazur
as Problem 43 in Stefan Banach's Scottish Book (1935). A more comprehensive
history of the Banacy-Mazur and other topological games may be found in 
Telgarsky's survey on the subject \cite{telgarsky}.

The original game was defined for subsets of the real line; however, 
we give a more general definition here.

@@

Non-trivial topological games are infinite, however, and many are indetermined
for certain spaces.

\begin{ex}
  Let $B$ be a Bernstein subset of the real line. Then $\bmgame{B}$ is
  undetermined.
\end{ex}

\begin{proof}
  It can be shown that $B$ is a Baire space, and we will soon see that 
  $\pl E\not\win \bmgame{X}$ characterizes Baire spaces. Also, if $\sigma$
  is a winning strategy for $\pl N$ in $\bmgame{Y}$ for $Y\subseteq X$, it can 
  be shown that $Y$ contains a closed uncountable set in $X$. 
  Thus $\pl N\not\win \bmgame{B}$.
\end{proof}

@@

The presence or absence of a winning strategie for a player in a topological
game characterizes a property of the topological space in question.

A classical result follows.

\begin{thm}
$\pl E\not\win \bmgame{X}$ if and only if $X$ is a Baire space. \cite{haworth}
\end{thm}

@@

(TODO: )
